Digital Twins for Ocean Robots

### 2024-11-27 paper/paper.tex
update table
update code snippets

% JuliaCon proceedings template
\documentclass{juliacon}[12pt]
\setcounter{page}{1}

@@

\begin{table}
\tbl{Ocean observing platforms targeted by \pkg{OceanRobots.jl}, and associated data structures (or blank if not yet implemented).}{
\begin{tabular}{|l||r|}\hline
Platform Type & Data Structure\\\hline\hline
surface drifters & \struct{SurfaceDrifter}, \struct{CloudDrift} \\
drifting profilers & \struct{ArgoFloat} \\
moored buoys & \struct{OceanSite}, \struct{NOAAbuoy} \\
sea gliders & \struct{Gliders} \\
expendable bathy-thermographs & \tbd \\
sail drones & \tbd \\
\hline
research vessel data & CCHDO \\
ships of opportunity data & \tbd \\
marine mammals & \tbd \\\hline
\end{tabular}}
\label{tab:robots}
\end{table}

@@

\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:ArgoCode},
    caption={Download and visualize one Argo float data as in Fig.~\ref{fig:Argo_Float}.}
]
using OceanRobots, ArgoData, CairoMakie
argo=read(ArgoFloat(),wmo=6900900)
fig=plot(argo,option=:standard)
\end{lstlisting}

@@

\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:IndDispCode},
    caption={Simulate surface drifter pathways in the Gulf of Mexico (Fig.~\ref{fig:drifters_speed}) from flow fields $u,v$ and initial positions $x,y$.}
]
using Drifters, DataFrames

dT=6*3600 #6 hours
nt=120*86400/dT #120 days

T=(0.,dT)
F=FlowFields(u=u,v=v,period=T)
I=Individuals(F,x,y)

[solve!(I,T.+dT*(n-1)) for n in 1:nt]
trajectories=groupby(I,:ID)
\end{lstlisting}

>>>>

% JuliaCon proceedings template
\documentclass{juliacon}[12pt]
\setcounter{page}{1}
\usepackage[utf8]{inputenc}

@@

\begin{table}
\tbl{Ocean observing platforms targeted by \pkg{OceanRobots.jl}, and associated data structures (or blank if not yet implemented).}{
\begin{tabular}{|l||r|}\hline
Platform Type & Data Structure\\\hline\hline
surface drifters & \struct{SurfaceDrifter}, \struct{CloudDrift} \\
drifting profilers & \struct{ArgoFloat} \\
moored buoys & \struct{OceanSite}, \struct{NOAAbuoy} \\
sea gliders & \struct{Gliders} \\
expendable bathy-thermographs & \tbd \\
sail drones & \tbd \\
\hline
research vessel data & \struct{CCHDO} \\
ships of opportunity data & \tbd \\
marine mammals & \tbd \\\hline
\end{tabular}}
\label{tab:robots}
\end{table}

@@

\begin{lstlisting}[
    language = Julia,
%    numbers=left,
    label={lst:ArgoCode},
    caption={Download and visualize one Argo float data as in Fig.~\ref{fig:Argo_Float}.}
]
using OceanRobots, ArgoData, CairoMakie;
argo=read(ArgoFloat(),wmo=6900900);
fig=plot(argo,option=:standard)
\end{lstlisting}

@@

\begin{lstlisting}[
    language = Julia,
    label={lst:IndDispCode},
    caption={Simulate surface drifter pathways in the Gulf of Mexico (Fig.~\ref{fig:drifters_speed}) from flow fields $u,v$ and initial positions $x,y$. 
    Visualization code is provided in the \pkg{Drifters.jl} documentation.}
]

using JLD2, CairoMakie, Drifters, OceanRobots;
P=Drifters.Gulf_of_Mexico_setup();
F=FlowFields(u=P.u,v=P.v,period=P.T);
I=Individuals(F,P.x0,P.y0);
[solve!(I,P.T .+P.dT*(n-1)) for n in 1:P.nt]
\end{lstlisting}
